Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-02 paper/galsize_paper.tex
Reorganized results subsections

@@

Much more successful is the profile co-evolution model shown with the solid curves in Figure \ref{fig:clustering_ratio_upshot}. The strongly negative clustering ratios predicted by the assumption of profile co-evolution can be understood in terms of the same features discussed above. Figure \ref{fig:coevolutionmodel} shows that at fixed $\mpeak,$ larger galaxies will occupy halos with larger $\rspeak.$ Since halo concentration $c=\rvir/R_{\rm s},$ this implies that high-concentration galaxies will tend to host smaller galaxies. Both satellites and splashback centrals have higher concentration than true centrals, another manifestation of assembly bias, and so the assumption of profile co-evolution naturally results in an enhancement of the clustering ratios beyond the $\rvir-$only model.

\subsection{Satellite Mass Loss}
\label{subsec:orphan_stripping}

We conclude this section with a discussion of Figure \ref{fig:strippingorphans}, which provides an estimate of how satellite mass stripping and orphan galaxies impact size-dependent clustering ratios. In the $\mstar-$stripping model described in \S\ref{subsubsec:strippingmodel}, satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations. This naturally results in an enhancement of size differences between satellites and centrals, and the dot-dashed curves in Figure \ref{fig:strippingorphans} show that produces the expected sign of the effect on the clustering ratios. The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\rvir-$only model. We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.

@@

>>>>

\subsection{Size-Mass Scaling Relation}
\label{subsec:one_point_function}

@@

\subsection{Failure of $\mstar-$based Models}
\label{subsec:orphan_stripping}

We conclude this section with a discussion of Figure \ref{fig:strippingorphans}, which provides an estimate of how satellite mass stripping and orphan galaxies impact size-dependent clustering ratios. In the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel}, satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations. This naturally results in an enhancement of size differences between satellites and centrals, and the dot-dashed curves in Figure \ref{fig:strippingorphans} show that produces the expected sign of the effect on the clustering ratios. The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\mstar-$only model. We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.

@@

\subsection{The Role of Morphology and Color}
\label{subsec:colormorph}
